---
title: 'Reproducible Research: Peer Assessment 1'
output:
  html_document:
    keep_md: yes
  pdf_document: default
---
```{r}


```

###Loading and preprocessing the data

```{r processingData,echo=TRUE, results='hide'}
setwd("C:/Users/Fooglee/Work/RepData_PeerAssessment1")
activty=read.csv("activity/activity.csv",na.string="NA",stringsAsFactor=F)
activty$date<-as.Date(strptime(activty$date,"%Y-%m-%d"))
ttlStpsDay<-tapply(activty$steps,activty$date,sum)
hist(ttlStpsDay,xlab = "Total number of steps",breaks = 10,main = "Total number of steps taken each day")

```
     
### What is mean total number of steps taken per day?
```{r}
mn=mean(ttlStpsDay,na.rm=T)
md=median(ttlStpsDay,na.rm = T)
```
Mean of total number of steps per day (ignoring NA values) is `r mn`  
Median of total number of steps per day (ignoring NA values) is `r md`

### What is the average daily activity pattern?

```{r}
library(ggplot2)
agr<-aggregate(x = list(mnstps=activty$steps),by=list(intrvl=activty$interval),FUN = mean,na.rm=T)
plot(x = agr$intrvl, y=agr$mnstps,type="l",xlab = "5 minutes Interval", ylab = "Average number of steps taken",main ="Average Number of Steps Taken Averaged Across All Days",xlim=c(0,2500),ylim=c(0,200))

```

### Imputing missing values

```{r}
naVals= sum(is.na(activty$steps))
```
Number of NA values = `r naVals`

The following code replaces NA values. It repaces NA values with next days mean

```{r}
ttlStpsMean<-tapply(activty$steps,activty$date,mean,na.rm=T)

for (i in 1:length(ttlStpsMean)){
  if(is.na(ttlStpsMean[i])){
    j=i
    while(T){
      j<-j+1
      if(j>length(ttlStpsMean)){
        j=0;
        next
      }
      if(!is.na(ttlStpsMean[j])){
        ttlStpsMean[i]<-ttlStpsMean[j];
        break
      }
    }
  }
}
noNAactivty<-activty;
noNAactivty$steps[is.na(noNAactivty$steps)]<-ttlStpsMean[as.character(noNAactivty$date[is.na(noNAactivty$steps)])]

ttlStpsNoNADay<-tapply(noNAactivty$steps,noNAactivty$date,sum)
hist(ttlStpsNoNADay,xlab = "Total number of steps",breaks = 10,main = "Total number of steps taken each day")
```

```{r}
mnn=mean(ttlStpsNoNADay)
mdd=median(ttlStpsNoNADay)
```
Mean of total number of steps per day (replacing NA values) is `r mnn`  
Median of total number of steps per day (replacing NA values) is `r mdd`

### Are there differences in activity patterns between weekdays and weekends?

```{r}
weekend=c("Sunday","Saturday")
noNAactivty$weekTime<-as.factor(ifelse(weekdays(noNAactivty$date) %in% weekend,"weekend","weekday"))


agrgd<-aggregate(x=list(steps=noNAactivty$steps),by = list(intrvl=noNAactivty$interval, weektime=noNAactivty$weekTime),mean)

library("lattice")
p <- xyplot(agrgd$steps ~ intrvl | factor(weektime), data=agrgd, 
            type = 'l' ,
            main="Average Steps Taken agregated Across All Weekday or Weekend",
            xlab="Interval",
            ylab="Average Number of Steps Taken")
print (p) 
```
